%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

  %---------------------------------------------------------

  \cventry
  {DevOps Developer} % Job title
  {Qingdao Ruishi Yanchuang Network Technology Co., Ltd. · On-Call} % Organization
  {Qingdao, Shandong, China} % Location
  {Aug 2021 - Present} % Date(s)
  {
    \begin{cvitems} % Description(s) of tasks/responsibilities
      \item {Implemented and maintained CI/CD pipelines using Jenkins and GitLab CI, reducing deployment time by 40\% and increasing release frequency.}
      \item {Designed and implemented a comprehensive monitoring and alerting system using Prometheus and Grafana, improving system reliability and reducing downtime by 30\%.}
      \item {Optimized cloud infrastructure costs by implementing auto-scaling policies and right-sizing resources, resulting in a 20\% reduction in monthly AWS expenses.}
      \item {Conducted regular security audits and implemented best practices, enhancing the overall security posture of the company's applications and infrastructure.}
    \end{cvitems}
  }

  \vspace{5mm}

  \cventry
  {Java Developer} % Job title
  {Qingdao Eastsoft Communication Technology Co., Ltd. · Permanent Full-time} % Organization
  {Qingdao, Shandong, China} % Location
  {Aug 2023 - Feb 2024} % Date(s)
  {
    \begin{cvitems} % Description(s) of tasks/responsibilities
      \item {Customized and extended Kingdee EAS financial sharing platform, enhancing project management and media management modules through secondary development, resulting in a 25\% improvement in project tracking efficiency.}
      \item {Developed ITR mobile services using Spring, Spring MVC, MyBatis, and Redis, implementing RESTful APIs that increased mobile app performance by 40\%.}
      \item {Managed full software development lifecycle for 3 major projects, from requirements analysis to deployment, reducing time-to-market by an average of 2 weeks per project.}
      \item {Collaborated with cross-functional teams using agile methodologies, increasing sprint completion rate from 80\% to 95\% over 6 months.}
      \item {Optimized database queries and implemented Redis caching, reducing average response time for critical features by 30\% and improving overall system performance.}
    \end{cvitems}
  }

  \vspace{5mm}

  %---------------------------------------------------------
  \cventry
  {Java Developer} % Job title
  {Qingdao Youshirui Network Technology Co., Ltd. · Permanent Full-time} % Organization
  {Qingdao, Shandong, China} % Location
  {May 2019 - Jul 2021} % Date(s)
  {
    \begin{cvitems} % Description(s) of tasks/responsibilities
      \item {Developed and maintained core functionalities for an online learning system using React, SpringBoot, and Alibaba Cloud, demonstrating versatility in working with diverse tech stacks and cloud platforms.}
      \item {Implemented RESTful APIs and microservices architecture to improve system modularity and scalability, resulting in a 35\% increase in application performance.}
      \item {Collaborated with cross-functional teams to design and implement new features, contributing to a 25\% increase in user engagement.}
      \item {Optimized database queries and implemented caching mechanisms, reducing average response time by 40\%.}
      \item {Led a team of 3 junior developers, providing mentorship and code reviews to improve overall code quality and team productivity.}
    \end{cvitems}
    % \begin{cvsubentries}
    %   \cvsubentry{}{KNOX(Solution for Enterprise Mobile Security) Penetration Testing}{Sep. 2013}{}
    %   \cvsubentry{}{Smart TV Penetration Testing}{Mar. 2011 - Oct. 2011}{}
    % \end{cvsubentries}
  }

  \vspace{5mm}
  \cventry
  {Java Developer} % Job title
  {Qingdao Lianxin Network Technology Service Co., Ltd. · Permanent Full-time} % Organization
  {Qingdao, Shandong, China} % Location
  {Mar 2018 - Feb 2019} % Date(s)
  {
    \begin{cvitems} % Description(s) of tasks/responsibilities
      \item {Developed new collection system architecture using Spring Boot and Spring Cloud for modular design and code reuse.}
      \item {Implemented performance tracking module, learning center module, and search center module.}
      \item {Designed and coded modules with focus on modularity and code reuse to enable efficient system enhancement.}
      \item {Collaborated with team to deliver collection system that met requirements for scalability and extensibility.}
    \end{cvitems}
  }

  \vspace{5mm}

  \cventry
  {Java Developer} % Job title
  {Qingdao Full Time Fitness Health Management Co., Ltd. · Permanent Full-time} % Organization
  {Qingdao, Shandong, China} % Location
  {Aug 2022 - Jan 2023} % Date(s)
  {
    \begin{cvitems} % Description(s) of tasks/responsibilities
      \item {Developed and implemented a member management system using Java and Spring framework, improving gym operations efficiency by 30\%.}
      \item {Designed and integrated a real-time workout tracking feature into the existing mobile app using RESTful APIs, resulting in a 25\% increase in daily active users within the first month of launch.}
    \end{cvitems}
  }
  %---------------------------------------------------------
\end{cventries}
